Solent region: Test Maps

### 2021-07-30 Solent_Mapping_v2.Rmd
Title for non dom gas diff 2010 and 2019
Tried to add the difference in fuel pov 2012- 2018 for LA but something has gone wrong

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2019}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```
### Difference in proportion Fuel Poverty 2012 to 2019
```{r Creating the idfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2019
#Red indicates an increase in fuel poverty from 2012 to 2019
fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
```
```{r Mapping the iddference in fuel poverty from 2012 to 2019}
merged_df$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov20192012dif <- merge(la_sf_data,merged_df)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov20192012dif$pcFP <- as.numeric(la_merged_Fuelpov20192012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov20192012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
```
# Mapping the Middle Layer Super Output Areas (MSOA)
## Mapping Domestic
### Mapping the Electricity Consumption

@@

>>>>

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2019}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```
### Difference in proportion Fuel Poverty 2012 to 2018 (BROKEN)
```{r Creating the difference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Red indicates an increase in fuel poverty from 2012 to 2018
#2018 has to be used as the metric for measuring fuel poverty changed in 2019
fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`

merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
names(merged_dfla)
merged_dfla$pc_diff <-merged_dfla$pc2018la - merged_df$pc2012la
```
```{r Mapping the difference in fuel poverty from 2012 to 2018}
merged_dfla$lad18cd <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov20182012dif <- merge(la_sf_data,merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov20182012dif$pcFP <- as.numeric(la_merged_Fuelpov20182012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov20182012dif) +
  geom_sf(aes(fill = pc_diffla)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
```
# Mapping the Middle Layer Super Output Areas (MSOA)
## Mapping Domestic
### Mapping the Electricity Consumption

@@

here here here
